Refinements for open pNets

### 2021-07-19 2021-Refinement/paper/refinementarticle.tex
example

\usepackage{amsmath,amssymb}
%\usepackage{amsthm}
%\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{external}
\usepackage{hyperref}
\AtBeginDocument{\renewcommand\setminus{\smallsetminus}}

@@

Establishing equivalences and refinement relations between programs is an important mean for 
verifying the correctness of programs, by formaly proving the relation between a specification and an implementation, 
proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
behaviors of a modified program simulate those of to the source one.

In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
behavioral models for communicationg systems. Open automata may have "holes" modeling elements of their
context, and can be composed by instanciation of the holes. This allows for a compositional approach for
verification of their behavior, essential to address proofs about large realistic systems.

We define several varriants of refinement between systems including either equal or different sets of holes, and 
show under which conditions these refinements are preserved by composition of open automata. We also discuss
the relations between these refinements and the existence of deadlocks.
We iluustrate these notions on several simple use-cases.

@@

Some related work on other models than open automata introduce refinement relations.
In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
Here the refinement relation does not consider action refinement as valid but it should be done in future work.
Also they check how LTL properties are preserved or combined using ther refinement which we do not do.
However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
Their relation additionally prevents deadlock and livelocks.
The compositon is also extended to synchronised composition which is more expressive.
In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition.

@@

\begin{figure}
\centering
\input{Traffic_Lights_Controller.tex}
\vrule
\input{Traffic_Lights_Full.tex}
\caption{TL}
\label{fig:TL}
\end{figure}

>>>>

\usepackage{amsmath,amssymb}
%\usepackage{amsthm}
%\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{external}
\usepackage{hyperref}
\usepackage{nccrules}
\AtBeginDocument{\renewcommand\setminus{\smallsetminus}}

@@

Establishing equivalences and refinement relations between programs is an important mean for 
verifying the correctness of programs, by formally proving the relation between a specification and an implementation, 
proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
behaviors of a modified program simulate those of to the source one.

In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
behavioral models for communicating systems. Open automata may have "holes" modeling elements of their
context, and can be composed by instanciation of the holes. This allows for a compositional approach for
verification of their behavior, essential to address proofs about large realistic systems.

We define several variants of refinement between systems including either equal or different sets of holes, and 
show under which conditions these refinements are preserved by composition of open automata. We also discuss
the relations between these refinements and the existence of deadlocks.
We illustrate these notions on several simple use-cases.

@@

Some related work on other models than open automata introduce refinement relations.
In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
Here the refinement relation does not consider action refinement as valid but it should be done in future work.
Also they check how LTL properties are preserved or combined using their refinement which we do not do.
However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
Their relation additionally prevents deadlock and livelocks.
The composition is also extended to synchronised composition which is more expressive.
In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition.

@@

As an example, the traffic light system  that controls  
 traffic at the intersection of a busy highway. In Figure \ref{fig:tls} we model it as open automaton and abstract the timer   as  Holes: a controller and a counter.

\begin{figure}
\centering
\input{Traffic_Lights_Spec.tex}
\caption{The specification of a traffic light system}
\label{fig:tls}
\end{figure}

\begin{figure}
%\centering
\input{Traffic_Lights_Controller.tex}
\input{Traffic_Lights_Register.tex}
\caption{On the left: An example of controller agent; On the right: An example of counter agent}
\label{fig:tlh}
\end{figure}

This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
It is supposed to be a single traffic light.

\begin{figure}
\centering
\input{Traffic_Lights_Full.tex}
\caption{The full traffic lights system}
\label{fig:tlf}
\end{figure}
